---
title: "Nobel gender bias"
author: Per Lunnemann
date: 31/01/2019
output: html_notebook
---

This document is intended as supporting material for the paper "Gender Bias in Nobel Prizes" https://arxiv.org/abs/1810.07280, with the entire code base for the calculation.

```{r  package_options, include=FALSE, warning = FALSE}
knitr::opts_chunk$set(fig.width=12, 
                      fig.height=8, 
                      echo=TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```
```{r, include=FALSE}
library(rstan, quietly = TRUE)
library(ggplot2, quietly = TRUE)
library(dplyr, quietly = TRUE)
library(ggmcmc, quietly = TRUE)
library(purrr, quietly = TRUE)
library(tibble, quietly = TRUE)

theme_Publication <- function(base_size=10L, darkTheme = FALSE) {
  library(grid)
  library(ggthemes)
  txtColor <- ifelse(darkTheme, 'white', 'black')
  lineColor <- ifelse(darkTheme, 'white', 'black')
  backgroundColor <- ifelse(darkTheme, 'black', 'white')
  panelBackgroundColor <- ifelse(darkTheme, "#333333", 'white')
  theme_foundation(base_size=base_size)+
      theme(plot.title = element_text(face = "bold",
                                      size = rel(1.0), hjust = 0.5),
            text = element_text(),
            panel.background = element_rect(colour = NA, fill = panelBackgroundColor),
            plot.background = element_rect(colour = NA,  fill = ifelse(darkTheme, 'black',NA)),
            panel.border = element_rect(colour = ifelse(darkTheme, 'black',NA)),
            axis.title = element_text(face = "bold",size = rel(0.9), color = txtColor),
            axis.title.y = element_text(angle=90,vjust =2, colour = txtColor),
            axis.title.x = element_text(vjust = -0.2, colour = txtColor),
            axis.text = element_text(colour = txtColor), 
            axis.line = element_line(colour = lineColor),
            axis.ticks = element_line(colour = lineColor),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            legend.key = element_rect(colour = NA, fill = backgroundColor),
            legend.title = element_text(size = rel(0.9), colour = txtColor),
            legend.text = element_text(size = rel(0.9), colour = txtColor),
            legend.background = element_rect(fill = backgroundColor),
            legend.box.background = element_rect(fill = backgroundColor),
            plot.margin=unit(c(2,2,2,2),"mm"),
            strip.background=element_rect(colour=ifelse(darkTheme, "#666666", "#f0f0f0"), fill=ifelse(darkTheme, "#666666", "#f0f0f0")),
            strip.text = element_text(face="bold", colour=txtColor)
      )
}

scale_fill_Publication <- function(...){
  library(scales)
  discrete_scale("fill",
                 "Publication",
                 manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
}

scale_colour_Publication <- function(...){
  library(scales)
  discrete_scale("colour",
                 "Publication",
                 manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
}

saveFigs <- FALSE
darkTheme <- FALSE
myggsaver <- function(gg, filename, width = 5,height = 3){
  fpath <- file.path(getwd(), 'figs', filename)
  filetype <- unlist(strsplit(x = filename, split = '\\.'))[2]
  ggsave(gg,filename = fpath,device = filetype, width = width,height = height)
}
```


# Loading of gender ratio data
We load the data from The National Research Foundation that describes the US faculty members gender ratio within various scientific fields. The grouping is slightly different from the categories of Nobel prizes, so we do a little renaming and regrouping. Notably, we assume that "Social sciences" can be exchanged with the subset "Economics" and "Life Science" is exchanged for "Physiology or Medicin". 
```{r Loading gender ratio, fig.retina = TRUE, warning = FALSE}
allDF <- read.csv('genderDistribution.csv')

ratioDF <- allDF %>% 
  gather(key='subject', value = 'value', -Year,-gender,-position) %>% 
  spread(key = gender, value = value)

# relabel
ratioDF <- ratioDF %>% mutate(prize = case_when(subject == 'Physical.sciences' ~ 'Physics', 
                                                subject == "Social.sciences" ~  'Economics', 
                                                subject == "Life.sciences" ~  'PhysMed', 
                                                TRUE ~ as.character(NA)
                                                )) %>%
                                mutate(ratio = female/both)

# copy physics into chemistry assuming ratio in chemistry is the same
chemDF <- ratioDF %>% filter(prize == 'Physics') %>% mutate(prize='Chemistry')

ratioDF <- full_join(ratioDF, chemDF)

gg <- ratioDF %>% 
  ggplot(aes(x=Year, y = ratio, color = position))+
  geom_point()+geom_line()+
  facet_wrap(subject~., scales='free_y')+
  theme_Publication(darkTheme = darkTheme)+
  scale_colour_Publication()

if(saveFigs){
  myggsaver(gg, 'genderRatios.pdf', width = 7, height = 4)
}
gg
```


# Load Nobel prize statistics

First we load the number of laurates within each field for each year seperated into gender
```{r}

nobelW <- read.csv('femaleNobelsL.csv')
head(nobelW)
# put in a long format
nobelW <- nobelW %>% gather(key=subject, value=value, -Year) %>%  
  separate(col = c('subject'), into = c('prize','gender'), sep='_') %>% 
  filter(gender!='all') %>% 
  select(-gender)
```

Next we extract the total number of Nobel laurates as taken from https://www.nobelprize.org :
```{r}
nobelDF <- read.csv(file = 'nobelLaurates.csv', encoding = 'Latin-1', stringsAsFactors = F)
head(nobelDF)
```

We notice that multiple names are separated by a `;`, and use that to count how many Nobel prizes were given per year per field. 
```{r}
nobelDF <- nobelDF %>% 
  rowwise() %>% 
  mutate_at( vars(-Year), 
             .funs = function(x) if_else(x == '???' | tolower(x) == 'none',
                                         0L, 
                                         length(strsplit(x, split=';')[[1]])) )  %>% 
  ungroup() %>% 
  as.data.frame() %>% 
  gather(key=prize, value = nbl, -Year)
head(nobelDF)
```


Now combine that with the number of female laureates:

```{r}
allNobelDF <- right_join(nobelDF,nobelW) %>% 
  rename(nbl_f=value) %>% 
  mutate(prize = if_else(prize=="Physiology.or.Medicine" ,'PhysMed', prize))

gg <- allNobelDF %>% mutate(nbl_m=nbl-nbl_f) %>% gather(key=key, value=value,nbl_m, nbl_f) %>% 
  ggplot(aes(x=Year, y=value, fill=key))+
  geom_bar(stat="identity")+
  facet_grid(prize~. , scales='free_y')+ ylab('Total')+
  scale_fill_brewer(palette = "Set1",name = 'Nobel laurates', labels=c("Female","Male"))+
  theme_Publication(darkTheme = TRUE)

if(saveFigs){
  myggsaver(gg = gg, filename = 'nobelLaurateBarPlot.pdf')
}
gg

```

So we can now join the data containing information on the gender ratio (`ratioDF`) and data counting the nobel laureates.
```{r}
totDF <- right_join(allNobelDF,ratioDF, by=c('Year','prize'))
sample_n(totDF,10)
```

We notice that most values of `nbl` and `nbl_f` are `NA` since we only have gender ratio data back untill year `r min(ratioDF$Year)`. To accomodate for this we shall do some extrapolation back in time. 

# Extrapolation
We shall extraplotate assuming a logistic function for each scientific field of the for
$$
f(y) = \frac{A}{1+\exp[(y-y_0)/g]}
$$
where $y$ is year and $y_0$ is a fit parameter such that $f(y_0) = A/2$. Finally, $g$ is a fit variable that determines the characteristic growth time. 
```{r}
# The function to fit
 myFitFunction <- function(df){
  nls(data = df, 
      formula = ratio~A/(1+exp(-(Year-2000-y00)/g))+off, 
      start = list(A = 0.5, g = 10, y00 = 10, off = 0.01), 
      lower=c(0,0.1,-30,0.0), 
      upper=c(1,20,30,0.2),
      control = list(maxiter = 50), 
      algorithm = 'port')
}

# The predictor function
myPredictorWithDelay <- function(fitObj, delay){
  year <- 1901:2019
  y <- year-delay
  y_i <- predict(fitObj, newdata=list(Year=y))
  return(data.frame(Year = year, ratioEx = y_i))
}

```

Once we have created the fit function we are now ready to do the extrapolation. We do this by grouping by prize and position, and subsequently fit and extrapolate.
```{r, warning=FALSE}
extrapolateRatio <- function(totDF, delay = 10){ #Make function that given totDF returns DF with extrapolated ratios
  by_prize <- totDF %>% filter(!is.na(prize)) %>% group_by(prize, position) %>% nest() 
  by_prize <- by_prize %>% mutate(model = purrr::map(.x = data,.f =  myFitFunction))
  by_prize <- by_prize %>% mutate(ratio_ex = map(.x = model, .f = function(x) myPredictorWithDelay(x,delay=delay)))
  ratioExDF <- unnest(by_prize,ratio_ex)
  return(ratioExDF)
}

# plot ratio data
ratioExDF4Plot <- extrapolateRatio(totDF, delay = 0)
gg <- full_join(ratioExDF4Plot, ratioDF) %>% 
  filter(position == 'senior' & !is.na(prize), prize !='Chemistry')  %>% 
  rename(Field = prize ) %>% 
  mutate(Field = factor(Field, levels = c('Economics','Physics','PhysMed') )) %>%
  mutate(ratioEx = if_else(Field=='Economics' & Year < 1969, as.numeric(NA), ratioEx)) %>% # Economics prize first awarded in 1969
  ggplot(aes(x=Year, color= Field))+
  geom_line(aes(y=ratioEx))+
  geom_point(aes(y=ratio))+
  theme_Publication(darkTheme = darkTheme)+
  scale_colour_Publication(labels = c('Economics'="Social Sciences", 'Physics'="Physical Sciences", 'PhysMed' = "Life Sciences" ), name = 'Field')+
  ylab('Gender ratio r')

if(saveFigs){
  myggsaver(gg, filename = 'ratioVsYear.pdf')
}

gg
```

We notice that "Social Sciences" only goes back to 1969 since the economics prize was not awarded untill then.

Now, finally, we can merge in the extrapolated values keeping only extrapolated values for those years we do not have data on the ratio. In this case, we fix the delay to 15, thus implying that most Nobel prize worthy achievements were on average carried out 15 years before the  prize was given. 
```{r}
#substitute ratio whith no data with the extrapolated ones
ratioExDF <- extrapolateRatio(totDF, delay = 15)
mydf <- full_join(ratioExDF, allNobelDF, intersect(colnames(ratioExDF), colnames(allNobelDF))) %>% 
                   left_join( . , ratioDF, by = intersect(colnames(.), colnames(ratioDF))) %>% 
  mutate(ratio = if_else(is.na(ratio), ratioEx, ratio))
```

# Setting up the data for STAN
The last step needed is converting the data into a format suitable for STAN. 
We would need the ratio `r`, the number of female laureates `y`, the total number of laureates `total`, and finally decide on what position to choose (senior, junior or all). In this case we choose senior
```{r stan data}
# generate data/matrices for STAN 
whichPosition <- 'senior'
year <- 1901:2018
year_test <- rep(2019)

r <- mydf %>% filter(position == whichPosition) %>%  
  select(Year, prize, ratio) %>% 
  spread(prize, ratio) %>% 
  arrange(Year) %>% 
  filter(Year %in% year) %>%
  select(-Year) %>% 
  as.matrix()
rownames(r) <- sort(unique(year))

num_test_points <- 1
r_test <- mydf %>% filter(position == whichPosition) %>%  
  select(Year, prize, ratio) %>% 
  spread(prize, ratio) %>% 
  arrange(Year) %>% 
  filter(Year %in% year_test) %>%
  select(-Year) # %>%

r_test <- r_test %>% mutate(dummy = 1L) %>% full_join(., tibble(dummy = rep(1L,num_test_points))) %>% select(-dummy) %>% as.matrix()


y <- mydf %>% filter(position == whichPosition) %>%  
  select(Year, prize, nbl_f) %>% 
  spread(prize, nbl_f) %>% 
  arrange(Year) %>% 
  filter(Year %in% year) %>%
  select(-Year) %>% 
  mutate_all(.funs = function(x) replace_na(x,0)) %>% 
  as.matrix()

total <- mydf %>% filter(position == whichPosition) %>%  
  select(Year, prize, nbl) %>% 
  spread(prize, nbl) %>% 
  arrange(Year) %>% 
  filter(Year %in% year) %>%
  select(-Year) %>% 
  as.matrix()

total_test <- data.frame(Chemistry=3, Economics=3, Physics=3, PhysMed=3) %>% mutate(dummy = 1L) %>% full_join(., tibble(dummy = rep(1L,num_test_points))) %>% select(-dummy) %>% as.matrix()

N <- nrow(total)
J <- ncol(total)

N_test <- nrow(total_test)

musd <- 1
alphasd <- 1
alphasd_center <- 1
alphasd_sigma <- 0.5
```

# Sampling assuming common $theta$



# Sampling fixed delay

```{r sampling, warning=FALSE, message=FALSE, results='hide'}
fit <-
  stan(
    file = 'myStanFile.stan',
    data = list(N = N, N_test = N_test,
                J = J,
                y = y, 
                r=r, r_test = r_test,
                total = total, total_test = total_test,
                samplePriors = FALSE,
                musd =musd,
                alphasd =alphasd),
    model_name =  'posterior',
    options(mc.cores = parallel::detectCores()),
    control = list(stepsize=0.01, adapt_delta=0.99),
    iter = 10000, chains = 2
  )

fitPrior <-
  stan(
    file = 'myStanFile.stan',
    data = list(N = N,
                J = J,
                y = y, 
                r=r, 
                total = total,
                samplePriors = TRUE,
                musd =musd,
                alphasd =alphasd),
    model_name =  'prior',
    options(mc.cores = parallel::detectCores()),
    control = list(stepsize=0.01, adapt_delta=0.99),
    iter = 5000, chains = 2
  )

```

# Regarding prediction
In the generated quantities we simulate, given the posterior value of $\alpha$, the outcome for year 2019. 
```{r}
hm <- rstan::extract(fit)
test <- as_tibble(drop(hm$y_test))
colnames(test) <- colnames(r)

#generate plot
plotDF <- test %>% 
  dplyr::sample_n(500) %>% # reduce samples for better visual clarity 
  tibble::rowid_to_column(var = 'sample') %>% 
  gather(key= 'prize', value='nblFemale', -sample) %>% 
  mutate(nblMale = 3-nblFemale) %>% 
  gather(key = 'gender', value = 'value', c('nblFemale','nblMale'))

gg <- plotDF %>% ggplot(aes(x=sample, y=value, fill=gender))+
  geom_bar(stat="identity")+
  facet_grid(prize~. , scales='free_y')+ ylab('Total')+
  scale_fill_brewer(palette = "Set1",name = 'Nobel laurates', labels=c("Female","Male"))+
  theme_Publication(darkTheme = darkTheme)

if(saveFigs){
  myggsaver(gg, filename = 'simulationBarPlot.pdf')
}
gg
```

```{r}
plotDF <- test %>% tibble::rowid_to_column(var = 'sample') %>% 
  gather(key= 'prize', value='nblFemale', -sample) %>% mutate(nblFemale = as.factor(nblFemale)) %>% group_by(prize, nblFemale) %>% summarise(value = n())
barPlot <- plotDF %>% 
  ggplot(aes( x='', y = value, fill=nblFemale)) + 
  geom_bar(stat = 'identity',width=1)+facet_wrap(~prize)
 
gg <- barPlot + coord_polar("y", start=0) + 
  geom_text(aes(label = paste0(round(value*100/nrow(test)), "%")), 
            colour='white', check_overlap  = TRUE,
            position = position_stack(vjust = 0.5))+
            # position = position_dodge(width = 0.0))+
  labs(x = NULL, y = NULL, fill = NULL)+
  theme_Publication(darkTheme = darkTheme)+
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())+
  scale_fill_brewer(type = 'div',
                    palette = 'YlGnBu',
                    direction = -1, 
                    name = 'Female laurates')

if(saveFigs){
  myggsaver(gg, filename = 'simulationPieChart.png',width = 5,height = 5)
}
gg
```

Let us have a look at the parameter $\log(\alpha)$ for the four scientific fields


```{r, warning=FALSE, echo = FALSE}
hm <- ggs(fit)
hmPrior <- ggs(fitPrior)

hmTot <- dplyr::bind_rows(list(Posterior=hm, Prior= hmPrior), .id = 'type') %>% 
  mutate(type=factor(type, levels=c('Prior','Posterior'))) %>% 
  mutate(Parameter = if_else(Parameter == 'lalpha[1]',colnames(r)[1], as.character(Parameter))) %>% 
  mutate(Parameter = if_else(Parameter == 'lalpha[2]',colnames(r)[2], as.character(Parameter))) %>% 
  mutate(Parameter = if_else(Parameter == 'lalpha[3]',colnames(r)[3], as.character(Parameter))) %>% 
  mutate(Parameter = if_else(Parameter == 'lalpha[4]',colnames(r)[4], as.character(Parameter)))
  
hmTot <- hmTot %>%  filter(Parameter %in% colnames(r))

hmPrior <- hmTot %>% filter(type == 'Prior') %>% filter(Parameter %in% colnames(r))
hmPosterior <- hmTot %>% filter(type == 'Posterior') %>% filter(Parameter %in% colnames(r))
gg <- hmTot %>%
  ggplot(aes(x=value))+
  geom_density(alpha=0.8,aes(fill=type))+
  facet_grid(Parameter~.)+
  theme_Publication(darkTheme = darkTheme)+
  scale_fill_manual(values = c("slategrey", "orange2"))+
  xlab(expression(log(alpha)))+ylab(expression(p( log(alpha)*"|"*r*","*delta)))

if(saveFigs){
  myggsaver(gg,filename = 'alphaPostvsPriorLog.pdf')
}

gg


```

```{r}
hmPosterior %>% group_by(Parameter) %>% summarise(b = 1-sum(as.numeric(value<0))/n())
```


Perhaps more intuitive to see it on a linear scale plotting $\alpha$

```{r, warning=FALSE, echo = FALSE}
# Do some plotting
hm <- ggs(fit)
hmPrior <- ggs(fitPrior)

hmTot <- dplyr::bind_rows(list(Posterior=hm, Prior= hmPrior), .id = 'type') %>% 
  mutate(type=factor(type, levels=c('Prior','Posterior'))) %>% 
  mutate(Parameter = if_else(Parameter == 'alpha[1]',colnames(r)[1], as.character(Parameter))) %>% 
  mutate(Parameter = if_else(Parameter == 'alpha[2]',colnames(r)[2], as.character(Parameter))) %>% 
  mutate(Parameter = if_else(Parameter == 'alpha[3]',colnames(r)[3], as.character(Parameter))) %>% 
  mutate(Parameter = if_else(Parameter == 'alpha[4]',colnames(r)[4], as.character(Parameter)))
  
hmTot <- hmTot %>%  filter(Parameter %in% colnames(r))

hmPrior <- hmTot %>% filter(type == 'Prior') %>% filter(Parameter %in% colnames(r))
hmPosterior <- hmTot %>% filter(type == 'Posterior') %>% filter(Parameter %in% colnames(r))
gg <- hmTot %>%
  ggplot(aes(x=value))+
  geom_density(alpha=0.8,aes(fill=type))+
  xlim(0,2.5)+
  facet_grid(Parameter~.)+
  theme_Publication(darkTheme = darkTheme)+
  scale_fill_manual(values = c("slategrey", "orange2"))+
  xlab(expression(alpha))+ylab(expression(p( alpha*"|"*r*","*delta)))

if(saveFigs){
  myggsaver(gg,filename = 'alphaPostvsPrior.pdf')
}

gg

```
```{r}
hmPosterior %>% group_by(Parameter) %>% summarise(b = 1-sum(as.numeric(value<1))/n())
```


# Delay dependence

In order to get an idea about the dependence of the choice of the "delay", we can repeat the whole procedure above, looping of each delay. Below we try out looping over delay ranging from 0 to 20:


```{r samplingSweep, warning = FALSE, message = FALSE, results='hide'}
delayArray <- 0:20
whichPosition <- 'senior'

fit <- list()
for (delay in delayArray){
  ratioExDF <- extrapolateRatio(totDF, delay = delay)
  # Merge it all into mydf 
  #substitute ratio whith no data with the extrapolated ones
  mydf <- left_join(full_join(ratioExDF, allNobelDF), ratioDF) %>% mutate(ratio = if_else(is.na(ratio), ratioEx, ratio))
  
  # generate data/matrices for STAN 
  r <- mydf %>% filter(position == whichPosition) %>%  
    select(Year, prize, ratio) %>% 
    spread(prize, ratio) %>% 
    arrange(Year) %>% 
    select(-Year) %>% 
    as.matrix()
  rownames(r) <- sort(unique(mydf$Year))
  
  y <- mydf %>% filter(position == whichPosition) %>%  
    select(Year, prize, nbl_f) %>% 
    spread(prize, nbl_f) %>% 
    arrange(Year) %>% 
    select(-Year) %>% 
    mutate_all(.funs = function(x) replace_na(x,0)) %>%
    as.matrix()
  
  total <- mydf %>% filter(position == whichPosition) %>%  
    select(Year, prize, nbl) %>% 
    spread(prize, nbl) %>% 
    arrange(Year) %>% 
    select(-Year) %>% 
    as.matrix()
  
  N <- nrow(total)
  J <- ncol(total)
  
  musd <- 1
  alphasd <- 1
  alphasd_center <- 1
  alphasd_sigma <- 0.5
  
  # Happy sampling 
  fit[[as.character(delay)]] <-
    stan(
      file = 'myStanFile.stan',
      data = list(N = N,
                  J = J,
                  y = y,
                  r=r,
                  total = total,
                  samplePriors = FALSE,
                  musd =musd,
                  alphasd =alphasd),
      model_name =  'example',
      options(mc.cores = parallel::detectCores()),
      control = list(stepsize=0.01, adapt_delta=0.99),
      iter = 2000, chains = 2
    )
  
}

```

We do a little bit of data massage before plotting
```{r  sweep data prep, warning = FALSE}

library(data.table)
sweeplist <- lapply(X = fit, FUN = ggs)

myMap <- list('alpha[1]' = colnames(r)[1], 'alpha[2]' = colnames(r)[2], 'alpha[3]' = colnames(r)[3], 'alpha[4]' = colnames(r)[4] )
myDT <- data.table::rbindlist(sweeplist,idcol =  'delay')[Parameter %like% '^alpha.[0-9].$'][, Parameter:=as.character(Parameter)][, delay:=as.numeric(delay)]
myDT[Parameter=='alpha[1]', Parameter := myMap[[1]]]
myDT[Parameter=='alpha[2]', Parameter := myMap[[2]]]
myDT[Parameter=='alpha[3]', Parameter := myMap[[3]]]
myDT[Parameter=='alpha[4]', Parameter := myMap[[4]]]
```

```{r delay sweep alpha violin plot, warning = FALSE, message = FALSE}
gg <- myDT[(delay%%2)==0,] %>% mutate(Parameter = factor(Parameter, levels = c('Economics','Physics','PhysMed','Chemistry') ))  %>% ggplot(aes(x=as.factor(delay), y=value, fill=Parameter))+
  geom_violin(draw_quantiles = c(0.5))+
  stat_summary(fun.y = "mean", geom = "point", shape=4, size=2, stroke = 1)+
  facet_grid(Parameter~. )+
  ylim(0,1)+ 
  xlab(expression('Lag '*delta*' [years]'))+
  ylab(expression(alpha))+
  theme_Publication(darkTheme = darkTheme)+scale_fill_Publication()
if(saveFigs){
  myggsaver(gg = gg, filename = 'meanVsDelayVioling.pdf')
}
gg
```

Intead of plotting a probability density distribution, we could also plot the probability of women being negatively biased. E.g. $P(\alpha\geq1)=\int_0^1 p(\alpha|r,\delta)\mathrm{d}\alpha$. For visual clarity, we shall instead plot probability of women being \emph{positively} biased, .e.g $P(\alpha\geq1)=1-\int_0^1 p(\alpha|r,\delta)\mathrm{d}\alpha$. Ofcourse, we don't need to fiddle with numerical integration. Instead we just utilize our samples (confident that our sampling has converged to the true distribution), and count those smaller than one and divide with total number of samples.

```{r delay sweep alpha line plot, warning = FALSE, message = FALSE}
gg <- myDT[,.(b = 1-sum(value <= 1)/.N), by = .(Parameter, delay)] %>% 
  as.data.frame() %>% 
  mutate(Parameter = factor(Parameter, levels = c('Economics','Physics','PhysMed','Chemistry') )) %>%
  ggplot(aes(y=b, x=delay, color=Parameter))+
  geom_line()+geom_point()+
  xlab(expression('Lag '*delta*' [years]'))+
  ylab(expression('P('*alpha*'>1)'))+
  theme_Publication(darkTheme = darkTheme)+scale_colour_Publication()+
  scale_colour_Publication( name = 'Scientific field')

if(saveFigs){
  myggsaver(gg = gg, filename = 'meanVsDelay.pdf')
}
gg
```
